---
title: "Meta-analysis notes"
author: "Jono Tuke"
date: "02/10/2019"
output: 
  html_document:
    theme: spacelab
    number_sections: yes
bibliography: meta-analysis.bib
citation_package: natbib 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, 
  fig.width = 12, 
  fig.asp = 0.618, 
  out.width = "100%",
  fig.align = "center", 
  root.dir = '../'
)
pacman::p_load(tidyverse)
```

Notes are based on @Schwarzer2015-jt


# Load libs

```{r}
pacman::p_load(tidyverse, meta, metafor)
```

# Read in data

```{r}
meta1  <- read_csv("../data/dataset01.csv")
meta1
```

So data is studies on comparing Nedocromil sodium with placebo for preventing exercise-induced bronchoconstriction

The columns are

- the author,
- the year of publication,
- Ne, the Number of patients (sample size) in the experimental treatment group,
- Me, the Mean response among the patients in the experimental group,
- Se, the Standard deviation of the response in the experimental group, and
- Nc, Mc and Sc the sample size, mean response and standard deviation in the
control patients.


## Perform meta-analysis

```{r}
meta1_MA  <- metacont(Ne, Me, Se, 
                       Nc, Mc, Sc, 
                       studlab = paste(author, year), 
                       data = meta1)
meta1_MA
```

```{r}
forest(meta1_MA, xlab = "Maximum % fall in FEV1")
```

# Continuous response

Two groups 

- experimental
- control

Usually have for each study $k$:

$$
\hat\mu_{ek}, s^2_{ek}, n_{ek},
\hat\mu_{ck}, s^2_{ck}, n_{ck}
$$

## Mean difference

Same scale

$$
\hat\mu_k = \hat\mu_{ek} - \hat\mu_{ck}
$$


```{r}
meta1 %>% 
  mutate(MD = Me - Mc, 
         lwr = MD - 1.96 * sqrt(Se^2 / Ne + Sc^2 / Nc),
         upr = MD + 1.96 * sqrt(Se^2 / Ne + Sc^2 / Nc))
```

## Standardised mean difference

Different scales

`meta` uses Hedge's g

$$
\hat{g}_k = (1 - 3/(4n_k-9)) \times
\frac{\hat\mu_{ek} - \hat\mu_{ck}}
{\sqrt{\frac{(n_{ek} - 1)s^2_{ek} + (n_{ck} - 1)s^2_{ck}}{n_k - 2}}}, 
$$
where

$$
n_k = n_{ek} + n_{ck}
$$

Also

$$
var(\hat{g}_k) = \frac{n_k}{n_{ek}n_{ck}} + 
\frac{\hat{g}^2_{k}}{2(n_k - 3.94)}
$$

```{r}
meta2  <- read_csv("../data/dataset02.csv")
meta2
```

```{r}
get_g  <- function(nc, ne, mc, me, sc, se){
  nk  <- nc + ne
  gk  <- (1 - 3 / (4 * nk - 9)) * 
    (me - mc) / sqrt(
      ((ne - 1) * se^2 + (nc - 1) * sc^2) / (nk - 2)
    )
}
```

```{r}
get_var_g  <- function(g, ne, nc){
  nk  <- nc + ne
  var_g  <- nk / (ne * nc) + g^2 / (2 * (nk - 3.94))
}
```

```{r}
meta2 %>% 
  mutate(
    g = get_g(Nc, Ne, Mc, Me, Sc, Se), 
    vg  = get_var_g(g, Ne, Nc), 
    lwr = g - 1.96 * sqrt(vg),
    upr = g + 1.96 * sqrt(vg)
  )
```

```{r}
metacont(Ne, Me, Se, 
         Nc, Mc, Sc, 
         data = meta2, 
         sm = "SMD", 
         studlab = author)
```

## Fixed Effect Model

$$
\hat\theta_k = \theta + \sigma_k\epsilon_k, \quad
\epsilon_k \stackrel{iid}{\sim}N(0,1).
$$

$$
\hat\theta_F = 
\frac{\sum^K_{k = 1}w_k \hat\theta_k}{
\sum^K_{k = 1}w_k
}, 
$$
where

$$
w_k = \frac1{\hat\sigma^2_k}
$$

$$
var(\hat\theta_F) = \frac1{\sum^K_{k = 1}w_k}
$$

```{r}
meta1  <- 
  meta1%>% 
  mutate(MD = Me - Mc, 
         v = Se^2 / Ne + Sc^2 / Nc, 
         w = 1 / v)
meta1
```

```{r}
weighted.mean(meta1$MD, w = meta1$w)
1 / sum(meta1$w)
meta1_MA$TE.fixed
meta1_MA$seTE.fixed^2
```

```{r}
meta1_MA
```


```{r}
meta1$w / sum(meta1$w)
```

## Random Effects Model

$$
\hat\theta_k = \theta + u_k + \sigma_k\epsilon_k, \quad \epsilon_k \stackrel{iid}{\sim}N(0, 1), u_k \stackrel{iid}{\sim}N(0, \tau^2)
$$

If study $k$ is rerun, then new $u_k$. _exchangeability assumption_

$$
Q = \sum^K_{k = 1}w_k(\hat\theta_k - \hat\theta_F)^2, w_k = \frac1{\hat\sigma_k^2}
$$
$Q$ is homogeneity test stat, heterogeneity statistic. 

$$
S = \sum^K_{k = 1}w_k - \frac{\sum^K_{k = 1}w_k^2}{\sum^K_{k = 1}w_k}
$$

1. $Q < (K - 1)$ set $\hat\tau^2$ to zero and $\hat\theta_R$ to $\hat\theta_F$.
2. Else
$$
\hat\tau^2 = \frac{Q - (K - 1)}{S} \text{ DerSimonian-Larid}
$$

$$
\hat\theta_R = 
\frac{\sum^K_{k = 1}w^*_k \hat\theta_k}{
\sum^K_{k = 1}w^*_k
}, 
$$

$$
var(\hat\theta_R) = \frac1{\sum^K_{k = 1}w^*_k}, 
$$

where

$$
w^*_k = \frac1{\hat\sigma^2_k + \hat\tau^2}
$$

## Prediction

```{r}
forest(meta1_MA, prediction = TRUE)
```


# References
